EDIpack: A generic and interoperable Lanczos-based solver for quantum impurity problems

### 2025-07-15 Reply_RefereeA.md

We thank the referee for their time and work in reviewing our
manuscript. In the following, we address point by point all the issues raised
in their reports.

<!-- *Exact diagonalization (ED) plays a vital role in the study of quantum impurity problems. In this work, the authors present an ED library and describe its usage in considerable detail. While it builds upon the previous EDIpack library, the manuscript introduces sufficient new developments to warrant a separate publication. Notably, several significant extensions and improvements are included, such as a unified framework for zero- and finite-temperature calculations for a wide range of impurity models; access to the full complex frequency plane; access to the Fock space and the ability to evaluate quantities like reduced density matrices; support for inequivalent impurities; integration with other programming languages and scientific libraries; and compatibility with widely used software suites such as TRIQS and w2dynamics.* -->

> *Overall, the paper is well written and highly detailed, allowing new users to install and utilize the library with ease. Furthermore, the comprehensive DMFT tests, demonstrated through a variety of examples and accompanied by corresponding scripts, provide excellent starting points for newcomers. I believe this work makes a valuable contribution to the community and am therefore pleased to recommend its publication in SciPost.*

We thank the referee for their positive assessment of our work and for recognizing its value in a more general context. We deeply appreciate their recommendation.

@@

> *On page 3, a large portion of paragraph 3, which introduces DMFT, lacks citations. For example, the authors mention the success of DMFT in capturing key features of various materials, including Mott insulators, heavy fermion compounds, and unconventional superconductors. It would be helpful to include relevant references here to guide interested readers toward further reading.
*

We agree with this comment of the referee. Although it is impossible to do justice to the wide literature accumulated over the years, we have made concerted efforts to incorporate key references that reflect the breadth and depth of research in this field. In the revised version, we have included several citations pertinent to DMFT across the discussed subjects, ensuring that foundational and more recent contributions are acknowledged. This approach aims to provide a balanced overview while addressing the referee's insightful comment.

> *Perhaps a sentence like “Section 6 provides the conclusions” was intended at the end of Section 1 but was inadvertently omitted?*

We sincerely appreciate the referee's prompt attention to this matter. We indeed  "inadvertently" overlooked a reference to Section 6, i.e. the conclusions, at the end of the introduction when discussing the manuscript's structure. We resolved this issue in the revised text by including the sentence:   
*"In Sec. 6 we present some concluding remarks and considerations."*

@@

> *The last display equation on page 10 seems incorrect, since the creation and annihilation operators do not appear to result in any particle being created or annihilated.*

We express our gratitude to the referee for bringing to our attention the discrepancy in the equations for the bosonic operators. In the revised manuscript, we have rectified this error by modifying the expressions on the right-hand side of the equations to account for the change in the bosonic number.

> *In Sec. 3.3, it appears that users must manually select one of the three provided symmetry configurations to perform block-diagonalization. Is there a plan to extend the code to automatically detect all relevant symmetries—especially in cases where orbitals or sites possess additional symmetries that would allow further block-diagonalization of the matrix?*

We acknowledge the referee’s observation. While the main code currently necessitates manual selection of one of the provided symmetry configurations, we recognize the value of automating the detection of all relevant symmetries. In fact, the Triqs interface ${\tt edipack2triqs}$ features an efficient algorithm to automatically recognize the symmetries of the problem and select the appropriate value for ${\tt ed\_mode}$. 
In the actual implementation of the Fortran API this can not be achieved, but we have plans to incorporate it in future release. In the current setup, this requires to accurately analyse the model Hamiltonian and the effective bath decomposition, as discussed in section 3.6, at initialization time.

At the same time, we are actively exploring development avenues that aim to integrate more sophisticated conservation laws, which would further reduce the matrix dimensions. We are confident that these enhancements would improve code’s flexibility and efficiency in managing systems characterized by intricate symmetries.

@@

> *On page 43, it is mentioned that the spectrum obtained from ED is “inherently spiky”. What is the value of the broadening parameter used in these simulations? Including this information in the main text may improve the clarity and reproducibility of the paper.*

We appreciate the referee's  observation. The extent of the Lorentzian broadening of the spectral poles is controlled by the input parameter `eps`. It is important to note that the value of `eps` is not fixed universally but rather is chosen based on the specific requirements of each case. In the particular examples discussed on page 43 of our manuscript, we have employed a broadening parameter of `eps = 0.01`, expressed in units of the half-bandwidth `D`.
In response to the referee's valuable suggestion, we have updated the manuscript  explicitly specifying the value of this broadening parameter.

### 2025-07-15 Reply_RefereeB.md

To enhance clarity and facilitate reader comprehension of its practical application, we have revised the text at this location. Specifically, we have included a forward reference to Section 5, where ${\tt ed\_set\_Hloc}$ is explicitly utilized in various application examples. These examples encompass the Hubbard model on the Bethe lattice (Section 5.1), the interacting Bernevig-Hughes-Zhang model (Section 5.5), and the Kane-Mele-Hubbard model (Section 5.6). These instances aim to elucidate both the structure of the input arguments and the context in which this function is commonly employed.

> *On p. 9, the discussion about the phonon cutoff sounds potentially a bit misleading. The cutoff is surely problem dependent, and there are (generalized) cases where the shift A\_m cannot be considered as a free parameter.*

We thank the referee for this observation. Indeed, the cutoff on the number of phonon excitations is inherently problem dependent and should be carefully adjusted in light of the specific electron-phonon coupling regime, the phonon frequency, and the interplay with electronic correlations. Furthermore, we agree that the shift $A_m$, while often treated as a tunable parameter in simplified models, is not always free to choose. In more general contexts, such as in first-principles-derived Hamiltonians or systems constrained by symmetry or external potentials, $A_m$ may be fixed by physical considerations or derived from the underlying microscopic model.

To reflect this more nuanced detail, we have revised the paragraph on page 9 to acknowledge that the shift $A_m$ is not universally a free parameter. This ensures that our discussion does not overgeneralise while aligning with the range of physical contexts in which EDIpack may be applied.

@@

*“From a computational perspective, constructing a symmetry sector amounts to defining an injective map $\mathcal{M} : \mathcal{S}_{\vec{Q}} \rightarrow \mathcal{F}_e$ that relates the consecutive indexing of the electronic states |i\rangle within a given symmetry sector $\mathcal{S}_{\vec{Q}}$ to the Fock states $|I_e\rangle$ in the electronic Fock space in their number representation. This map is typically implemented as a rank-1 integer array, whose size corresponds to the dimension of the sector $D^{\mathcal{S}}$.”*

This new formulation replaces the previous wording and makes explicit the distinction between the consecutive indexing of the sector states $|i\rangle$ and the Fock states in the integer-based occupation number representation $|I_e\rangle$. In doing so, we clarify that the mapping $\mathcal{M}$ is what connects the two encodings of the same physical state. We believe the revised text should eliminate the ambiguity the referee noted.

> *The motivation of including the code on p. 12 is unclear. What is the intention here?*

We thank the referee for raising this point. The code snippet on page 12 was originally included to illustrate the concrete implementation of the mapping from Fock states to symmetry sectors for different values of ${\tt ed\_mode}$. Our goal was to make explicit the internal logic used to construct the quantum number-conserving subspaces, bridging the gap between formal description and practical realization. Moreover, this code snippet is useful to understand the structure of the ${\tt sparse\_map}$ used to implement fast algorithm for the evaluation of the reduced impurity density matrix in Section 3.5.2.

@@

> *p. 16: GFmatrix is said to be a critical component for high-speed execution. Maybe it could be describe in more detail? In what way is it efficient? What does it mean it is multi-layed? In passing, it would be nice if the capitalization would be uniform, e.g. GFmatrix vs. gfmatrix (I understand that Fortran compiler does not care, but the human reader perhaps does).*

We thank the referee for pointing out the need for a clearer and more detailed description of the ${\tt gfmatrix}$ type, which indeed plays a central role in the performance of the code. In response, we have revised the corresponding section of the manuscript (page 16) to provide a more precise explanation of its structure and efficiency features.

The term multi-layered refers to the hierarchical organization of the ${\tt gfmatrix}$ object, which is essential for storing and accessing the analytic structure of correlation functions, i.e. the weights and the poles, in a flexible and scalable way. 
Specifically, the data are organized across three conceptual layers: (1) the many-body eigenstates of the Hamiltonian spectrum, (2) the amplitude channels associated to each such state, and (3) the set of poles and weights corresponding to physical excitations from this state. This structure is necessary to correctly represent the Lehmann decomposition of Green's functions and related objects, while still allowing dynamic access and manipulation during calculations.

The efficiency of ${\tt gfmatrix}$ stems from two main features. First, correlation functions do not need to be precomputed and stored on fixed frequency or time grids; instead, their values are computed on-the-fly at arbitrary complex arguments, allowing precise and flexible evaluation as required by different solvers or output formats. Second, memory usage is optimized by avoiding redundant storage. The internal design separates spectral data, and evaluation logic, allowing minimal overhead during the object construction and easing post-processing analysis. 
We recognize that the use of the term "high-performance" could be misleading and rephrases the paragraph on page 16 in a more precise way as

"*The module ${\tt ED\_GFMATRIX}$ implements the class ${\tt gfmatrix}$, which provides an efficient and flexible representation of DCFs. It is structured as a hierarchical, or {\it multilayered}, data container that organizes spectral weights and poles across three levels: (i) the initial eigenstate $|n\rangle$ of the Hamiltonian spectrum, (ii) the amplitude channel associated with this state, corresponding to the applied operator, and (iii) the set of excitations from $|n\rangle$, each characterized by a pole and its corresponding weight.  
This structure allows the ${\tt gfmatrix}$ class to simultaneously handle multiple initial states and operators, enabling on-the-fly evaluation of DCFs at arbitrary complex frequencies $z \in \mathbb{C}$. By avoiding precomputed grids and redundant storage this approach minimizes memory footprint and computational overhead. Through the use of ${\tt gfmatrix}$ EDIpack achieve and efficient memory management, consistent storage of spectral data, and high-performance post-processing.*"

@@

These listings are intended to complement the discussion by offering concrete examples that clarify how the formal logic is realized in code. Given the potential for confusion when dealing with basis state reconstruction and operator ordering in fermionic systems, we believe that these examples will be of interest and practical benefit to users aiming to extend or interface with the library.

> *p. 28: "as the nonsu2 and superc diagonalizations entail nontrivial subtleties in optimizing the off-diagonal components of X". What are these subtleties?*

We acknowledge that our brief comment reads a bit obscure while this point requires a more detailed, yet brief, discussion.

The bath optimization is a crucial step in the DMFT framework. Hence, to ensure EDIpack has a large degree of versatility while preserving robustness, we introduced several control parameters for the conjugate-gradient fit. A key one is the definition of the norm, or distance, between matrix functions appearing in Eq. 30.

While the choice of metric plays a limited role for matrix-valued functions with particularly symmetric structures, it can significantly impact the quality of the optimization in more general cases. 
The subtleties in optimizing the off-diagonal components in either ${\tt nonsu2}$ and ${\tt superc}$ diagonalizations arise from the complex interplay between these components’ physical characteristics and the picked optimization metric. 
In either case, the coexistence of components having a very different physical interpretation, e.g., anomalous terms, and/or spanning very different energy scales represents a serious challenge to the optimization of the bath. 
This requires careful tuning of the control parameters to ensure that the optimization does not disproportionately favor certain matrix elements over others, thereby maintaining the overall fidelity of the bath representation.
In this sense, introducing other norms, which ensure a better balance among the components, is a development line to improve EDIpack usage.

@@

> *As a general coding comment: would it be possible to remove use of global variables?*

We thank the referee for this general but important observation. In principle, it is indeed possible to eliminate the use of global variables by explicitly passing all data structures through subroutine arguments. However, in the context of Fortran, and similarly in other compiled languages, global variables (typically implemented via module-level variables) do not incur any performance or memory management penalties.

Their use in EDIpack is deliberate and serves to maintain clarity and modularity in the code, particularly for widely shared objects such as configuration parameters, system-wide operators, or state indexing data. Removing these global definitions would require passing a large number of arguments through deep call chains, which we believe would significantly increase code complexity, reduce readability, and introduce greater potential errors, without offering any computational or architectural advantages.

However, we recognise the importance of careful design in managing global memory, and we have ensured that such variables are encapsulated within dedicated modules with well defined scopes. Should it prove beneficial for future code maintainability or extension by third-party contributors, we are open to review and refine this aspect of the implementation.

@@

We thank the referee for carefully reviewing this section and pointing this out. Indeed, the variable ${\tt Wband}$ should not appear in the code listing, as it corresponds to ${\tt D}$, which is correctly defined earlier in the script.  Additionally, the variable ${\tt de}$ represents the energy grid spacing, computed as ${\tt de = 2D / Le}$, where Le is the number of energy points discretizing the Bethe lattice density of states. We have corrected the code listing accordingly to eliminate Wband and clarify the definition of de.

> *p. 42: "provides access to well-tested functions". This is unclear. Functions doing what?*

We thank the referee for pointing out the ambiguity in this sentence. Our intention was to clarify that, although the bath optimization problem is conceptually distinct from the core impurity diagonalization task, for which EDIpack was originally developed, nonetheless the package provides access to a well-tested implementation of the conjugate-gradient fitting procedure for the bath optimization. We have revised the sentence accordingly in the manuscript to make this connection and the role of these functions more explicit by writing:

*"Given the critical importance of this step, EDIpack provides access to a well-tested implementation of the conjugate gradient method for performing the bath optimization, ensuring stability and reproducibility of the results, even though this task remains conceptually distinct from the  diagonalization of the impurity problem, which remains the core focus of the package."*

### 2025-07-15 02_install.tex
Iterated Revision: AA, LC, IK, SG and GB. Ready to share to all authors.

  -D{\bf LONG\_PREFIX}          & Install directory (if & {\color{xkcdEmerald} $\sim$/opt/edipack/\textbackslash}\\
  &install prefix unset)&{\color{xkcdEmerald}TAG/\textbackslash} (\textit{e.g. 5.3.3})\\
  &&{\color{xkcdEmerald}PLAT/\textbackslash} (\textit{gnu/intel/...})\\
  &&{\color{xkcdEmerald}BRANCH} (\textit{branch name})\textbf{/}\\
  &&$\sim$/opt/edipack/custom \\
  -D{\bf USE\_MPI}       & MPI support  &  True\textbf{/}{\color{xkcdEmerald}False}\\
  -D{\bf WITH\_INEQ}   & Multi-impurities support & {\color{xkcdEmerald}True}\textbf{/}{False}\\
  -D{\bf VERBOSE}      & Verbose CMake output & {\color{xkcdEmerald}True}\textbf{/}{False}\\ 
  -D{\bf BUILD\_TYPE} & Compilation flags & {\color{xkcdEmerald}RELEASE}\textbf{/}TESTING\textbf{/}DEBUG \\
 \hline
\end{tabular}
\end{center}
%
The default target builds and installs both the main library and the C-bindings.
Separate build targets for each component are available. A recap message is printed at the end of the CMake configuration step to guide the user through the compilation, installation and OS loading process.

>>>>

  -D{\bf LONG\_PREFIX}          & Install directory (if & {\color{xkcdEmerald} $\sim$/opt/edipack/\textbackslash}\\
  &install prefix unset)&{\color{xkcdEmerald}TAG/\textbackslash} (\textit{e.g. 5.3.3})\\
  &&{\color{xkcdEmerald}PLAT/\textbackslash} (\textit{gnu/intel/...})\\
  &&{\color{xkcdEmerald}BRANCH} (\textit{branch name})\\
  &&$\sim$/opt/edipack/custom \\
  -D{\bf USE\_MPI}       & MPI support  &  True\textbf{/}{\color{xkcdEmerald}False}\\
  -D{\bf WITH\_INEQ}   & Multi-impurities support & {\color{xkcdEmerald}True}\textbf{/}{False}\\
  -D{\bf VERBOSE}      & Verbose CMake output & {\color{xkcdEmerald}True}\textbf{/}{False}\\ 
  -D{\bf BUILD\_TYPE} & Compilation flags & {\color{xkcdEmerald}RELEASE}\textbf{/}TESTING\textbf{/}DEBUG \\
 \hline
\end{tabular}
\end{center}
%
The default target builds and installs both the main library and the C-bindings.
Separate build targets for each component are available. A recap message is printed at the end of the CMake configuration step to guide the user through the compilation, installation and OS loading process.

### 2025-07-15 03_edipack2.tex
Iterated Revision: AA, LC, IK, SG and GB. Ready to share to all authors.

In many cases, one can reduce the number of excited phonons in the ground state, and
consequently the required cutoff, by appropriately choosing the shift $A_m$.
In practice one can use $A_m = \langle \hat{O}_m \rangle $ and redefine a shifted bosonic fields $\tilde{b}_m^{(\dagger)} = b_m^{(\dagger)} + \frac{\langle \hat{O}_m \rangle }{\omega_0}$. This choice would ensure that $\langle \tilde{b}_m^\dagger + \tilde{b}_m \rangle =0$ effectively reducing the number of phonons required for the calculation. Observables on the physical bosons are linked to the new one via the previous transformation.
{ \color{red} However, we stress that this is not always possible: in some generalized models or realistic systems derived from microscopic considerations, $A_m$ may be fixed and not a freely tunable parameter. In such cases, the phonon cutoff must be increased accordingly to ensure numerical convergence. SG: i would remove this part}
Although feasible, dealing with more than one phonon mode quickly becomes computationally very demanding, thus we will consider only one mode and we drop the $m$ index in the rest of this work.

@@

From a computational perspective, constructing a symmetry
sector amounts to defining an injective map
$\MM:\SS_{\vec{Q}}\rightarrow \FF_e$ that relates the consecutive indexing of the electronic states  $\ket{i}$
within a given symmetry sector $\SS_{\vec{Q}}$ to the Fock states $\ket{I_e}$ in the electronic Fock space in their number representation. 
This map is typically implemented as a rank-1 integer array, whose size corresponds to the dimension of the sector $D_{\SS_{\vec{Q}}}$. 
The global Fock state $\ket{I}=\ket{I_e}\ket{p}$, including the phonon part, is univocally determined by the relation: $I\to I_e + p\,2^{2 N_s}$.

@@

The module {\tt ED\_GFMATRIX} implements the class {\tt gfmatrix}, which provides an efficient and flexible representation of DCFs. It is structured as a hierarchical, or {\it multi-layered}, data container that organizes spectral weights and poles across three levels: (i) the initial eigenstate $\ket{n}$ of the Hamiltonian spectrum, (ii) the amplitude channel associated with this state, corresponding to the applied operator, and (iii) the set of excitations from $\ket{n}$, each characterized by a pole and its corresponding weight.
This structure allows the {\tt gfmatrix} class to simultaneously handle multiple initial states and operators, enabling on-the-fly evaluation of DCFs at arbitrary complex frequencies $z \in \mathbb{C}$. By avoiding precomputed grids and redundant storage this approach minimizes memory footprint and computational overhead. As a result, {\tt gfmatrix} is a core component of \NAME, essential for efficient memory management, consistent storage of spectral data, and high-performance post-processing.

>>>>

In many cases, one can reduce the number of excited phonons in the ground state, and
consequently the required cutoff, by appropriately choosing the shift $A_m$.
In practice one can use $A_m = \langle \hat{O}_m \rangle $ and redefine a shifted bosonic fields $\tilde{b}_m^{(\dagger)} = b_m^{(\dagger)} + \frac{\langle \hat{O}_m \rangle }{\omega_0}$. This choice would ensure that $\langle \tilde{b}_m^\dagger + \tilde{b}_m \rangle =0$ effectively reducing the number of phonons required for the calculation. Observables on the physical bosons are linked to the new one via the previous transformation.
% { \color{red} However, we stress that this is not always possible: in some generalized models or realistic systems derived from microscopic considerations, $A_m$ may be fixed and not a freely tunable parameter. In such cases, the phonon cutoff must be increased accordingly to ensure numerical convergence. SG: i would remove this part}
Although feasible, dealing with more than one phonon mode quickly becomes computationally very demanding, thus we will consider only one mode and we drop the $m$ index in the rest of this work.

@@

From a computational perspective, constructing a symmetry
sector amounts to defining an injective map
$\MM:\SS_{\vec{Q}}\rightarrow \FF_e$ that relates the consecutive indexing of the electronic states  $\ket{i}$
within a given symmetry sector $\SS_{\vec{Q}}$ to the Fock states $\ket{I_e}$ in the electronic Fock space in their number representation~\cite{Wallerberger2022PRR}. 
This map is typically implemented as a rank-1 integer array, whose size corresponds to the dimension of the sector $D_{\SS_{\vec{Q}}}$. 
The global Fock state $\ket{I}=\ket{I_e}\ket{p}$, including the phonon part, is univocally determined by the relation: $I\to I_e + p\,2^{2 N_s}$.

@@

The module {\tt ED\_GFMATRIX} implements the class {\tt gfmatrix}, which provides an efficient and flexible representation of DCFs. It is structured as a hierarchical, or {\it multi-layered}, data container that organizes spectral weights and poles across three levels: (i) the initial eigenstate $\ket{n}$ of the Hamiltonian spectrum, (ii) the amplitude channel associated with this state, corresponding to the applied operator, and (iii) the set of excitations from $\ket{n}$, each characterized by a pole and its corresponding weight.
This structure allows the {\tt gfmatrix} class to simultaneously handle multiple initial states and operators, enabling on-the-fly evaluation of DCFs at arbitrary complex frequencies $z \in \mathbb{C}$. By avoiding precomputed grids and redundant storage this approach minimizes memory footprint and computational overhead. Through the use of ${\tt gfmatrix}$ EDIpack achieve and efficient memory management, consistent storage of spectral data, and high-performance post-processing.

### 2025-07-15 05_examples.tex
Iterated Revision: AA, LC, IK, SG and GB. Ready to share to all authors.

   !Solver-specific arrays. Using Rank-5  
   allocate(Smats(Nspin,Nspin,Norb,Norb,Lmats))
   allocate(Delta(Nspin,Nspin,Norb,Norb,Lmats))
   allocate(Hloc(Nspin,Nspin,Norb,Norb))
   Hloc=0d0
   !...
   !Construct Bethe DOS using SciFortran
   allocate(Ebands(Le),Dbands(Le))
   Ebands = linspace(-D,D,Le,mesh=de)
   Dbands = dens_bethe(Ebands,Wband)*de
   !
   !EDIpack: Set impurity Hamiltonian
   call ed_set_hloc(Hloc)
\end{lstlisting}
\end{minipage}
%
\begin{minipage}[t]{0.49\linewidth}
\textbf{C++}
\begin{lstlisting}[style=cstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
#include <edipack_cbindings.h>
using namespace std;
//...
//Main variables
int Le = 1000;
int iloop = 0;
double wmixing = 0.5;
double D = 1.0;

@@

//Locally defined functions:
Ebands = linspace(-D,D,Le);
Dbands = dens_bethe(Ebands,Wband,de);

@@

The first two steps are handled directly by \NAME routines, while during the subsequent steps the 
 control returns to the user, who must implement the algebraic updates required to 
close the self-consistency loop and optimize the bath.
Given the 
critical importance of this optimization, \NAME provides access to 
well-tested functions, ensuring stability and reproducibility of 
results. Alternative optimization methods can also be employed as 
needed \cite{Mejuto-Zaera2020PRB,Huang2023PRB,Nakatsukasa2018SJOSC}. 
An example of implementation is provided in the following listings.

>>>>

   !Solver-specific arrays. Using Rank-5  
   allocate(Smats(Nspin,Nspin,Norb,Norb,Lmats))
   allocate(Delta(Nspin,Nspin,Norb,Norb,Lmats))
   allocate(Hloc(Nspin,Nspin,Norb,Norb))
   Hloc=0d0
   !...
   !Construct Bethe DOS using SciFortran
   !de = 2*D/(Le-1)
   allocate(Ebands(Le),Dbands(Le))
   Ebands = linspace(-D,D,Le,mesh=de)
   Dbands = dens_bethe(Ebands,D)*de
   !
   !EDIpack: Set impurity Hamiltonian
   call ed_set_hloc(Hloc)
\end{lstlisting}
\end{minipage}
%
\begin{minipage}[t]{0.49\linewidth}
\textbf{C++}
\begin{lstlisting}[style=cstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
#include <edipack_cbindings.h>
using namespace std;
//...
//Main variables
int Le = 1000;
int iloop = 0;
double wmixing = 0.5;
double D = 1.0;

@@

//Locally defined functions: de = 2*D/(Le-1)
Ebands = linspace(-D,D,Le);
Dbands = dens_bethe(Ebands,D,de);

@@

The first two steps are handled directly by \NAME routines, while during the subsequent steps the 
 control returns to the user, who must implement the algebraic updates required to 
close the self-consistency loop and optimize the bath.
Given the critical importance of this step, \NAME provides access to a well-tested implementation of the conjugate gradient method for performing the bath optimization, ensuring stability and reproducibility of the results, even though this task remains conceptually distinct from the  diagonalization of the impurity problem, which remains the core focus of the package.
Alternative optimization methods can also be employed as 
needed \cite{Mejuto-Zaera2020PRB,Huang2023PRB,Nakatsukasa2018SJOSC}. 
An example of implementation is provided in the following listings.
